SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2018-12-06 results.tex
Mostly related to images, methodology, typos etc
Updating Single Core Results
...to reflect simpoint weighted results

Figure~\ref{Fig:SPEC2017_1core} shows the IPC speedup obtained by PPF,
compared to BOP, DA-AMPM and SPP.  In the figure we have depicted selected
traces where PPF shows a noticeable improvement or shows some degradation,
along with the geometric mean improvement on the memory intensive subset of
SPEC CPU 2017, and finally for the complete SPEC CPU 2017 benchmark.  All the
results have been normalized to the baseline of no prefetching.

@@

PPF yields a geometric mean speedup of \textbf{42.8\%} over the baseline. 
This is equivalent to \textbf{7.8\%} over DA-AMPM, \textbf{9.7\%} over BOP 
and \textbf{6.92\%} over SPP.  Out of the 95 simpoints developed for SPEC 
CPU 2017, PPF nearly matches or outperforms most of the prefetchers on 91 
simpoints.  PPF fails to match the improvement offered by BOP only for 
{\tt 607.cactuBSSN\_s} and {\tt 654.roms\_s}.

At its peak, PPF manages a speedup of a factor of over \textbf{3.39x} on the
trace {\tt 602.gcc\_s-2226B}.  This also corresponds to speedup gain of
\textbf{60\%} over the next best prefetcher -- BOP.  In general, benchmarks
{\tt 603.bwaves\_s}, {\tt 605.mcf\_s}, {\tt 623. xalancbmk\_s} and {\tt
649.fotonik3d\_s} benefit the most from PPF, with the speedup over SPP ranging
from \textbf{10\% to 25\%}.

% djimenez: is this geometric mean? if so, say so.
% [EB] Resolved
On the full SPEC CPU 2017 suite, PPF improves the geometric mean IPC of 
the baseline by \textbf{20.9\%}, which is \textbf{3.44\%} better 
than the next best prefetcher -- SPP.
\newline

@@

\begin{figure}[ht]
\includegraphics[width=2.75in]{4CORE_IPC_PPF}
\caption{Speedup for 4-core SPEC CPU 2017}
\label{Fig:4Core_SPEC2017}
\end{figure}

@@

\begin{figure}[ht]
\includegraphics[width=2.75in]{8CORE_IPC_PPF}
\caption{Speedup for 8-core SPEC CPU 2017}
\label{Fig:8Core_SPEC2017}
\end{figure}

@@

%[EB] How to justify only a small margin over DA-AMPM?

@@

Figure~\ref{Fig:SPEC2006_1core} shows the speed-up achieved by BOP, SPP and
PPF on traces from SPEC CPU 2006, along with the overall geometric mean over
the whole suite and over a memory-intensive subset.  PPF provides a speedup of
\textbf{46.1\%} over the baseline on the memory intensive subset of SPEC CPU
2006 benchmark, giving an improvement of \textbf{6.66\%} over SPP and
\textbf{9.88\%} over DA-AMPM and \textbf{9.82} over BOP.  On the whole of 
the SPEC CPU 2006 suite, the speedup is \textbf{22.4\%}, an improvement 
of \textbf{3.34\%} over SPP.

>>>>

Figure~\ref{Fig:SPEC2017_1core} shows the IPC speedup obtained by PPF,
compared to BOP, DA-AMPM and SPP; for the individual SPEC CPU 2017 
applications, followed by memory intensive subset and finally the full
suite. All the results have been normalized to the baseline of no prefetching.

@@

PPF yields a geometric mean speedup of \textbf{27\%} over the baseline. 
This is equivalent to \textbf{4.63\%} over DA-AMPM, \textbf{4.61\%} over BOP 
and \textbf{3.78\%} over SPP. Out of the 95 simpoints developed for SPEC 
CPU 2017, PPF nearly matches or outperforms most of the prefetchers on 91 
simpoints. PPF fails to match the improvement offered by BOP only for 
{\tt 607.cactuBSSN\_s} and {\tt 654.roms\_s} traces.

At its peak, PPF manages a speedup of a factor of over \textbf{3.39x} on one of the
{\tt 602.gcc\_s} traces. This also corresponds to speedup gain of
\textbf{60\%} over the next best prefetcher for that trace -- BOP. In general, benchmarks
{\tt 603.bwaves\_s}, {\tt 605.mcf\_s}, {\tt 623. xalancbmk\_s} and {\tt
649.fotonik3d\_s} benefit the most from PPF, with the speedup over SPP ranging
from \textbf{10\% to 25\%}.

% djimenez: is this geometric mean? if so, say so.
% [EB] Resolved
On the full SPEC CPU 2017 suite, PPF improves the geometric mean IPC of 
the baseline by \textbf{15.24\%}, which is \textbf{2.27\%} better 
than the next best prefetcher -- SPP.
\newline

@@

\begin{figure}[ht]
\includegraphics[width=2.75in]{4Core_SPEC2017}
\caption{Speedup for 4-core SPEC CPU 2017}
\label{Fig:4Core_SPEC2017}
\end{figure}

@@

\begin{figure}[ht]
\includegraphics[width=2.75in]{8Core_SPEC2017}
\caption{Speedup for 8-core SPEC CPU 2017}
\label{Fig:8Core_SPEC2017}
\end{figure}

@@

@@

Figure~\ref{Fig:SPEC2006_1core} shows the speed-up achieved by BOP, SPP and
PPF on the memory intensive subset and the full SPEC CPU 2006 suite. 
PPF provides a speedup of \textbf{36.3\%} over the baseline on the 
memory intensive subset of SPEC CPU
2006 benchmark, giving an improvement of \textbf{6.1\%} over SPP and
\textbf{8.44\%} over DA-AMPM and \textbf{9.93} over BOP. On the whole of 
the SPEC CPU 2006 suite, the speedup is \textbf{19.6\%}, an improvement 
of \textbf{3.33\%} over SPP.
